Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-03-03 analysis/paper/paper.Rmd
Tried to pull all three of the biplots into one plot_grid, with mixed results. Currently in the process of working things out, might not be able to put all three plots into one plot_grid due to the sheer size and complexity of each plot, which does not seem to play well with cowplot.

# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$dorsal_cortext_group,
             palette = "npg", #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Dorsal Cortex Class") +  #adjust accordingly)
             coord_fixed(ratio = 1)+ #adjustable for variation-weighted plots
  theme(plot.title = element_blank())

@@

```{r excavation-unit-biplot, fig.cap="PCA biplot for flake shape and excavation unit."}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

# Mass PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$mass_group,
             palette = viridis::viridis(6), #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Mass\ncluster",  #adjust accordingly
            title = "Flake mass and flake shape") + 
             coord_fixed(ratio = 1) + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

>>>>

# ggplot2-based plot of the PCA results using a factoextra function
cortex_biplot <- fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$dorsal_cortext_group,
             palette = "npg", #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Dorsal Cortex Class") +  #adjust accordingly)
             coord_fixed(ratio = 1)+ #adjustable for variation-weighted plots
  theme(plot.title = element_blank())

@@

```{r excavation-unit-biplot, fig.cap="PCA biplot for flake shape and excavation unit."}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
excavation_unit_biplot <- fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

# Mass PCA
# ggplot2-based plot of the PCA results using a factoextra function
mass_biplot <- fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$mass_group,
             palette = viridis::viridis(6), #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Mass\ncluster",  #adjust accordingly
            title = "Flake mass and flake shape") + 
             coord_fixed(ratio = 1) + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

```{r}
library(cowplot)

plot_grid(
  cortex_biplot, NULL, NULL,  excavation_unit_biplot,  mass_biplot, NULL,
  ncol = 2,
  labels = c("A", NULL, NULL,"B","C",NULL),
  label_size = 12,
  align = "v",
  rel_heights = c(1.1,
                  1,
                  1.1,
                  4,
                  1,
                  1),
  rel_widths = c(2,
                 2,
                 2,
                 4,
                 2,
                 1))

#cortex_biplot + theme(plot.margin = unit(c(3,3,3,3), "lines"))
#excavation_unit_biplot
#mass_biplot

#plot_grid(
#  plot_a, NULL, plot_b
#  , nrow = 1
#  , rel_widths = c(1, 0.05, 1)
#  , labels = c("A", "", "B")
#)

    #      axis = "none",
   #       scale = 1,
   #       nrow = 3,
    #      ncol = 1,
   #       rel_widths = c(1,1,1),
   #       rel_heights = c(1,1,1)
